---
title: "Hoben Data"
output: word_document
always_allow_html: yes
---


```{r,include=FALSE}
setwd("/Users/Dil/Documents/Fall_2017/Research/psyco project")

library(mixtools)
library(fitdistrplus)
source("gammamixEMnew.R")
Hoben <- read.table("Hoben.txt",header=T)

#*******ratio between the second trial(age x+ of the kid) and the first trial(age x of the kid is considered*********#

#first time look
x1 <- Hoben[,15]/Hoben[,4] #Produces results in favor of fixed alpha
x1a=x1^1/3

#Second time look
x2 <- Hoben[,16]/Hoben[,5]


#Third time look
x3 <- Hoben[,17]/Hoben[,6]

#Fourth time look
x4 <- Hoben[,18]/Hoben[,7]

v1=cbind(x1,x2)
R1=v1^1/3

v2=cbind(x1,x2,x3)
R2=v2^1/3

v3=cbind(x1,x2,x3,x4)
R3=v3^1/3

BIC=function(ll,n,npar) -2*ll+log(n)*npar
```
## Bivariate normal for R1 and R2
```{r,include=FALSE}
#k=1(one componant bivariate normal)
library(mvtnorm)
v1.sigma=cov(cr_v1)
v1.mu=cbind(mean(cr_v1[,1]),mean(cr_v1[,2]))

v1.tmp = mvtnorm::dmvnorm(cr_v1,v1.mu,v1.sigma,log=T)
v1.k1.loglik=sum(v1.tmp)
v1.k1.BIC=BIC(v1.k1.loglik,98,5)


```
Expected Values 
```{r,echo=FALSE}
v1.mu
```
Variance-Covariance 
```{r,echo=FALSE}
v1.sigma
```
###Log Likelihhod
```{r,echo=FALSE}
v1.k1.loglik
```
###BIC
```{r,echo=FALSE}
v1.k1.BIC
```
## Two component bivariate normal for R1 and R2

```{r,include=FALSE}
#k=2 (Two componant bivariate normal)
set.seed(12)
out.cr_v1.k2=mvnormalmixEM(cr_v1, lambda = NULL, mu = NULL, sigma = NULL, k = 2,
              arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
              maxit = 10000, verb = FALSE)

v1.k2.lambda=out.cr_v1.k2[2][[1]]
v1.k2.mu1=out.cr_v1.k2[3][1][[1]][[1]]
v1.k2.mu2=out.cr_v1.k2[3][1][[1]][[2]]
v1.k2.sigma1=out.cr_v1.k2[4][1][[1]][[1]]
v1.k2.sigma2=out.cr_v1.k2[4][1][[1]][[2]]
v1.k2.loglik=out.cr_v1.k2[5][[1]]
v1.k2.BIC=BIC(v1.k2.loglik,98,11)

```
Mixing Proportions ($\lambda$) 
```{r,echo=FALSE}

v1.k2.lambda
```
###Component 1
Expected Values 
```{r,echo=FALSE}
v1.k2.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k2.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v1.k2.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k2.sigma2
```
###Log Likelihhod
```{r,echo=FALSE}
v1.k2.loglik
```
###BIC
```{r,echo=FALSE}
v1.k2.BIC
```

## Three component bivariate normal for R1 and R2
```{r,include=FALSE}
#k=3 (Three componant bivariate normal)
set.seed(13)
out.cr_v1.k3=mvnormalmixEM(cr_v1, lambda = NULL, mu = NULL, sigma = NULL, k = 3,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)

v1.k3.lambda=out.cr_v1.k3[2][[1]]
v1.k3.mu1=out.cr_v1.k3[3][1][[1]][[1]]
v1.k3.mu2=out.cr_v1.k3[3][1][[1]][[2]]
v1.k3.mu3=out.cr_v1.k3[3][1][[1]][[3]]
v1.k3.sigma1=out.cr_v1.k3[4][1][[1]][[1]]
v1.k3.sigma2=out.cr_v1.k3[4][1][[1]][[2]]
v1.k3.sigma3=out.cr_v1.k3[4][1][[1]][[3]]
v1.k3.loglik=out.cr_v1.k3[5][[1]]
v1.k3.BIC=BIC(v1.k3.loglik,98,17)
```

Mixing Proportions ($\lambda$) 
```{r,echo=FALSE}

v1.k3.lambda
```
###Component 1

Expected Values 
```{r,echo=FALSE}
v1.k3.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k3.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v1.k3.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k3.sigma2
```
###Component 3
Expected Values 
```{r,echo=FALSE}
v1.k3.mu3
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k3.sigma3
```
###Log Likelihhod
```{r,echo=FALSE}
v1.k3.loglik
```
###BIC
```{r,echo=FALSE}
v1.k3.BIC
```
##Four component bivariate normal for R1 and R2

```{r,include=FALSE}
#k=4 (Four componant bivariate normal)
set.seed(14)
out.cr_v1.k4=mvnormalmixEM(cr_v1, lambda = NULL, mu = NULL, sigma = NULL, k = 4,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)

v1.k4.lambda=out.cr_v1.k4[2][[1]]
v1.k4.mu1=out.cr_v1.k4[3][1][[1]][[1]]
v1.k4.mu2=out.cr_v1.k4[3][1][[1]][[2]]
v1.k4.mu3=out.cr_v1.k4[3][1][[1]][[3]]
v1.k4.mu4=out.cr_v1.k4[3][1][[1]][[4]]
v1.k4.sigma1=out.cr_v1.k4[4][1][[1]][[1]]
v1.k4.sigma2=out.cr_v1.k4[4][1][[1]][[2]]
v1.k4.sigma3=out.cr_v1.k4[4][1][[1]][[3]]
v1.k4.sigma4=out.cr_v1.k4[4][1][[1]][[4]]
v1.k4.loglik=out.cr_v1.k4[5][[1]]
v1.k4.BIC=BIC(v1.k4.loglik,98,23)
```

Mixing Proportions ($\lambda$) 
```{r,echo=FALSE}

v1.k4.lambda
```
###Component 1

Expected Values 
```{r,echo=FALSE}
v1.k4.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k4.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v1.k4.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k4.sigma2
```
###Component 3
Expected Values 
```{r,echo=FALSE}
v1.k4.mu3
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k4.sigma3
```
###Component 4
Expected Values 
```{r,echo=FALSE}
v1.k4.mu4
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k4.sigma4
```
###Log Likelihhod
```{r,echo=FALSE}
v1.k4.loglik
```
###BIC
```{r,echo=FALSE}
v1.k4.BIC
```
## Five component bivariate normal for R1, R2
```{r,include=FALSE}
#k=5 (Five componant bivariate normal)
set.seed(16)
out.cr_v1.k5=mvnormalmixEM(cr_v1, lambda = NULL, mu = NULL, sigma = NULL, k = 5,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)

v1.k5.lambda=out.cr_v1.k5[2][[1]]
v1.k5.mu1=out.cr_v1.k5[3][1][[1]][[1]]
v1.k5.mu2=out.cr_v1.k5[3][1][[1]][[2]]
v1.k5.mu3=out.cr_v1.k5[3][1][[1]][[3]]
v1.k5.mu4=out.cr_v1.k5[3][1][[1]][[4]]
v1.k5.mu5=out.cr_v1.k5[3][1][[1]][[5]]
v1.k5.sigma1=out.cr_v1.k5[4][1][[1]][[1]]
v1.k5.sigma2=out.cr_v1.k5[4][1][[1]][[2]]
v1.k5.sigma3=out.cr_v1.k5[4][1][[1]][[3]]
v1.k5.sigma4=out.cr_v1.k5[4][1][[1]][[4]]
v1.k5.sigma5=out.cr_v1.k5[4][1][[1]][[5]]
v1.k5.loglik=out.cr_v1.k5[5][[1]]
v1.k5.BIC=BIC(v1.k5.loglik,98,29)
```

Mixing Proportions ($\lambda$) 
```{r,echo=FALSE}

v1.k5.lambda
```
###Component 1

Expected Values 
```{r,echo=FALSE}
v1.k5.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k5.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v1.k5.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k5.sigma2
```
###Component 3
Expected Values 
```{r,echo=FALSE}
v1.k5.mu3
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k5.sigma3
```
###Component 4
Expected Values 
```{r,echo=FALSE}
v1.k5.mu4
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k5.sigma4
```
###Component 5
Expected Values 
```{r,echo=FALSE}
v1.k5.mu5
```
Variance-Covariance 
```{r,echo=FALSE}
v1.k5.sigma5
```
###Log Likelihhod
```{r,echo=FALSE}
v1.k5.loglik
```
###BIC
```{r,echo=FALSE}
v1.k5.BIC
```
## Trivariate normal for R1,R2 and R3
```{r,include=FALSE}
#k=1 (One componant trivariate normal)
library(mvtnorm)
v2.sigma=cov(cr_v2)
v2.mu=cbind(mean(cr_v2[,1]),mean(cr_v2[,2]),mean(cr_v2[,3]))

v2.tmp = mvtnorm::dmvnorm(cr_v2,v2.mu,v2.sigma,log=T)
v2.k1.loglik=sum(v2.tmp)
v2.k1.BIC=BIC(v2.k1.loglik,98,9)
```
Expected Values 
```{r,echo=FALSE}
v2.mu
```
Variance-Covariance 
```{r,echo=FALSE}
v2.sigma
```
###Log Likelihhod
```{r,echo=FALSE}
v2.k1.loglik
```
###BIC
```{r,echo=FALSE}
v2.k1.BIC
```

## Two component trivariate normal for R1, R2 and R3

```{r,include=FALSE}
 #k=2 (Two componant trivariate normal)
set.seed(320)
out.cr_v2.k2=mvnormalmixEM(cr_v2, lambda = NULL, mu = NULL, sigma = NULL, k = 2,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)

v2.k2.lambda=out.cr_v2.k2[2][[1]]
v2.k2.mu1=out.cr_v2.k2[3][1][[1]][[1]]
v2.k2.mu2=out.cr_v2.k2[3][1][[1]][[2]]
v2.k2.sigma1=out.cr_v2.k2[4][1][[1]][[1]]
v2.k2.sigma2=out.cr_v2.k2[4][1][[1]][[2]]
v2.k2.loglik=out.cr_v2.k2[5][[1]]
v2.k2.BIC=BIC(v2.k2.loglik,98,19)


```
Mixing Proportions ($\lambda$) 
```{r,echo=FALSE}

v2.k2.lambda
```
###Component 1
Expected Values 
```{r,echo=FALSE}
v2.k2.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k2.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v2.k2.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k2.sigma2
```
###Log Likelihhod
```{r,echo=FALSE}
v2.k2.loglik
```
###BIC
```{r,echo=FALSE}
v2.k2.BIC
```
## Three component trivariate normal for R1, R2 and R3

```{r,include=FALSE}
#k=3 (Three componant trivariate normal)
set.seed(23)
out.cr_v2.k3=mvnormalmixEM(cr_v2, lambda = NULL, mu = NULL, sigma = NULL, k = 3,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)

v2.k3.lambda=out.cr_v2.k3[2][[1]]
v2.k3.mu1=out.cr_v2.k3[3][1][[1]][[1]]
v2.k3.mu2=out.cr_v2.k3[3][1][[1]][[2]]
v2.k3.mu3=out.cr_v2.k3[3][1][[1]][[3]]
v2.k3.sigma1=out.cr_v2.k3[4][1][[1]][[1]]
v2.k3.sigma2=out.cr_v2.k3[4][1][[1]][[2]]
v2.k3.sigma3=out.cr_v2.k3[4][1][[1]][[3]]
v2.k3.loglik=out.cr_v2.k3[5][[1]]
v2.k3.BIC=BIC(v2.k3.loglik,98,29)
```
Mixing Proportions ($\lambda$) 
```{r,echo=FALSE}

v2.k3.lambda
```
###Component 1
Expected Values 
```{r,echo=FALSE}
v2.k3.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k3.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v2.k3.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k3.sigma2
```
###Component 3
Expected Values 
```{r,echo=FALSE}
v2.k3.mu3
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k3.sigma3
```
###Log Likelihhod
```{r,echo=FALSE}
v2.k3.loglik
```
###BIC
```{r,echo=FALSE}
v2.k3.BIC
```
## Four component trivariate normal for R1, R2 and R3
```{r,include=FALSE}
#k=4 (Four componant trivariate normal)
set.seed(24)
out.cr_v2.k4=mvnormalmixEM(cr_v2, lambda = NULL, mu = NULL, sigma = NULL, k = 4,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)

v2.k4.lambda=out.cr_v2.k4[2][[1]]
v2.k4.mu1=out.cr_v2.k4[3][1][[1]][[1]]
v2.k4.mu2=out.cr_v2.k4[3][1][[1]][[2]]
v2.k4.mu3=out.cr_v2.k4[3][1][[1]][[3]]
v2.k4.mu4=out.cr_v2.k4[3][1][[1]][[4]]
v2.k4.sigma1=out.cr_v2.k4[4][1][[1]][[1]]
v2.k4.sigma2=out.cr_v2.k4[4][1][[1]][[2]]
v2.k4.sigma3=out.cr_v2.k4[4][1][[1]][[3]]
v2.k4.sigma4=out.cr_v2.k4[4][1][[1]][[4]]
v2.k4.loglik=out.cr_v2.k4[5][[1]]
v2.k4.BIC=BIC(v2.k4.loglik,98,39)
```
###Component 1
Expected Values 
```{r,echo=FALSE}
v2.k4.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k4.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v2.k4.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k4.sigma2
```
###Component 3
Expected Values 
```{r,echo=FALSE}
v2.k4.mu3
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k4.sigma3
```
###Component 4
Expected Values 
```{r,echo=FALSE}
v2.k4.mu4
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k4.sigma4
```
###Log Likelihhod
```{r,echo=FALSE}
v2.k4.loglik
```
###BIC
```{r,echo=FALSE}
v2.k4.BIC
```
## Five component trivariate normal for R1, R2 and R3
```{r,include=FALSE}
#k=5 (Five componant trivariate normal)
set.seed(26)
out.cr_v2.k5=mvnormalmixEM(cr_v2, lambda = NULL, mu = NULL, sigma = NULL, k = 5,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)

v2.k5.lambda=out.cr_v2.k5[2][[1]]
v2.k5.mu1=out.cr_v2.k5[3][1][[1]][[1]]
v2.k5.mu2=out.cr_v2.k5[3][1][[1]][[2]]
v2.k5.mu3=out.cr_v2.k5[3][1][[1]][[3]]
v2.k5.mu4=out.cr_v2.k5[3][1][[1]][[4]]
v2.k5.mu5=out.cr_v2.k5[3][1][[1]][[5]]
v2.k5.sigma1=out.cr_v2.k5[4][1][[1]][[1]]
v2.k5.sigma2=out.cr_v2.k5[4][1][[1]][[2]]
v2.k5.sigma3=out.cr_v2.k5[4][1][[1]][[3]]
v2.k5.sigma4=out.cr_v2.k5[4][1][[1]][[4]]
v2.k5.sigma5=out.cr_v2.k5[4][1][[1]][[5]]
v2.k5.loglik=out.cr_v2.k5[5][[1]]
v2.k5.BIC=BIC(v2.k5.loglik,98,49)

```
Mixing Proportions ($\lambda$) 
```{r,echo=FALSE}

v2.k5.lambda
```
###Component 1

Expected Values 
```{r,echo=FALSE}
v2.k5.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k5.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v2.k5.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k5.sigma2
```
###Component 3
Expected Values 
```{r,echo=FALSE}
v2.k5.mu3
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k5.sigma3
```
###Component 4
Expected Values 
```{r,echo=FALSE}
v2.k5.mu4
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k5.sigma4
```
###Component 5
Expected Values 
```{r,echo=FALSE}
v2.k5.mu5
```
Variance-Covariance 
```{r,echo=FALSE}
v2.k5.sigma5
```
###Log Likelihhod
```{r,echo=FALSE}
v2.k5.loglik
```
###BIC
```{r,echo=FALSE}
v2.k5.BIC
```
## Multivariate normal for R1, R2, R3 and R4
```{r,include=FALSE}
#k=1 (One componant tetravariate normal)
library(mvtnorm)
v3.sigma=cov(cr_v3)
v3.mu=cbind(mean(cr_v3[,1]),mean(cr_v3[,2]),mean(cr_v3[,3]),mean(cr_v3[,4]))

v3.tmp = mvtnorm::dmvnorm(cr_v3,v3.mu,v3.sigma,log=T)
v3.k1.loglik=sum(v3.tmp)
v3.k1.BIC=BIC(v3.k1.loglik,98,14)
```
Expected Values 
```{r,echo=FALSE}
v3.mu
```
Variance-Covariance 
```{r,echo=FALSE}
v3.sigma
```
###Log Likelihhod
```{r,echo=FALSE}
v3.k1.loglik
```
###BIC
```{r,echo=FALSE}
v3.k1.BIC
```
## Two component multivariate normal for R1, R2, R3 and R4
```{r,include=FALSE}
#k=2 (Two componant tetravariate normal)
set.seed(4200)
out.cr_v3.k2=mvnormalmixEM(cr_v3, lambda = NULL, mu = NULL, sigma = NULL, k = 2,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)

v3.k2.lambda=out.cr_v3.k2[2][[1]]
v3.k2.mu1=out.cr_v3.k2[3][1][[1]][[1]]
v3.k2.mu2=out.cr_v3.k2[3][1][[1]][[2]]
v3.k2.sigma1=out.cr_v3.k2[4][1][[1]][[1]]
v3.k2.sigma2=out.cr_v3.k2[4][1][[1]][[2]]
v3.k2.loglik=out.cr_v3.k2[5][[1]]
v3.k2.BIC=BIC(v3.k2.loglik,98,29)
```
Mixing Proportions ($\lambda$) 
```{r,echo=FALSE}

v3.k2.lambda
```
###Component 1
Expected Values 
```{r,echo=FALSE}
v3.k2.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k2.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v3.k2.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k2.sigma2
```
###Log Likelihhod
```{r,echo=FALSE}
v3.k2.loglik
```
###BIC
```{r,echo=FALSE}
v3.k2.BIC
```
## Three component multivariate normal for R1, R2, R3 and R4
```{r,include=FALSE}
#k=3 (Three componant tetravariate normal)
set.seed(33)
out.cr_v3.k3=mvnormalmixEM(cr_v3, lambda = NULL, mu = NULL, sigma = NULL, k = 3,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)

v3.k3.lambda=out.cr_v3.k3[2][[1]]
v3.k3.mu1=out.cr_v3.k3[3][1][[1]][[1]]
v3.k3.mu2=out.cr_v3.k3[3][1][[1]][[2]]
v3.k3.mu3=out.cr_v3.k3[3][1][[1]][[3]]
v3.k3.sigma1=out.cr_v3.k3[4][1][[1]][[1]]
v3.k3.sigma2=out.cr_v3.k3[4][1][[1]][[2]]
v3.k3.sigma3=out.cr_v3.k3[4][1][[1]][[3]]
v3.k3.loglik=out.cr_v3.k3[5][[1]]
v3.k3.BIC=BIC(v3.k3.loglik,98,44)

```
Mixing Proportions ($\lambda$) 
```{r,echo=FALSE}

v3.k3.lambda
```
###Component 1
Expected Values 
```{r,echo=FALSE}
v3.k3.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k3.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v3.k3.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k3.sigma2
```
###Component 3
Expected Values 
```{r,echo=FALSE}
v3.k3.mu3
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k3.sigma3
```
###Log Likelihhod
```{r,echo=FALSE}
v3.k3.loglik
```
###BIC
```{r,echo=FALSE}
v3.k3.BIC
```
## Four component multivariate normal for R1, R2, R3 and R4
```{r,include=FALSE}
#k=4 (Four componant tetravariate normal)
set.seed(400)
out.cr_v3.k4=mvnormalmixEM(cr_v3, lambda = NULL, mu = NULL, sigma = NULL, k = 4,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)


v3.k4.lambda=out.cr_v3.k4[2][[1]]
v3.k4.mu1=out.cr_v3.k4[3][1][[1]][[1]]
v3.k4.mu2=out.cr_v3.k4[3][1][[1]][[2]]
v3.k4.mu3=out.cr_v3.k4[3][1][[1]][[3]]
v3.k4.mu4=out.cr_v3.k4[3][1][[1]][[4]]
v3.k4.sigma1=out.cr_v3.k4[4][1][[1]][[1]]
v3.k4.sigma2=out.cr_v3.k4[4][1][[1]][[2]]
v3.k4.sigma3=out.cr_v3.k4[4][1][[1]][[3]]
v3.k4.sigma4=out.cr_v3.k4[4][1][[1]][[4]]
v3.k4.loglik=out.cr_v3.k4[5][[1]]
v3.k4.BIC=BIC(v3.k4.loglik,98,59)
```

###Component 1
Expected Values 
```{r,echo=FALSE}
v3.k4.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k4.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v3.k4.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k4.sigma2
```
###Component 3
Expected Values 
```{r,echo=FALSE}
v3.k4.mu3
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k4.sigma3
```
###Component 4
Expected Values 
```{r,echo=FALSE}
v3.k4.mu4
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k4.sigma4
```
###Log Likelihhod
```{r,echo=FALSE}
v3.k4.loglik
```
###BIC
```{r,echo=FALSE}
v3.k4.BIC
``` 

## Five component multivariate normal for R1, R2, R3 and R4

```{r,echo=FALSE}
#k=5(Five componant tetravariate normal)
set.seed(46)
out.cr_v3.k5=mvnormalmixEM(cr_v3, lambda = NULL, mu = NULL, sigma = NULL, k = 5,
                           arbmean = TRUE, arbvar = TRUE, epsilon = 1e-08, 
                           maxit = 10000, verb = FALSE)
v3.k5.lambda=out.cr_v3.k5[2][[1]]
v3.k5.mu1=out.cr_v3.k5[3][1][[1]][[1]]
v3.k5.mu2=out.cr_v3.k5[3][1][[1]][[2]]
v3.k5.mu3=out.cr_v3.k5[3][1][[1]][[3]]
v3.k5.mu4=out.cr_v3.k5[3][1][[1]][[4]]
v3.k5.mu5=out.cr_v3.k5[3][1][[1]][[5]]
v3.k5.sigma1=out.cr_v3.k5[4][1][[1]][[1]]
v3.k5.sigma2=out.cr_v3.k5[4][1][[1]][[2]]
v3.k5.sigma3=out.cr_v3.k5[4][1][[1]][[3]]
v3.k5.sigma4=out.cr_v3.k5[4][1][[1]][[4]]
v3.k5.sigma5=out.cr_v3.k5[4][1][[1]][[5]]
v3.k5.loglik=out.cr_v3.k5[5][[1]]
v3.k5.BIC=BIC(v3.k5.loglik,98,74)
```
###Component 1
Expected Values 
```{r,echo=FALSE}
v3.k5.mu1
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k5.sigma1
```
###Component 2
Expected Values 
```{r,echo=FALSE}
v3.k5.mu2
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k5.sigma2
```
###Component 3
Expected Values 
```{r,echo=FALSE}
v3.k5.mu3
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k5.sigma3
```
###Component 4
Expected Values 
```{r,echo=FALSE}
v3.k5.mu4
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k5.sigma4
```
###Component 5
Expected Values 
```{r,echo=FALSE}
v3.k5.mu5
```
Variance-Covariance 
```{r,echo=FALSE}
v3.k5.sigma5
```
###Log Likelihhod
```{r,echo=FALSE}
v3.k5.loglik
```
###BIC
```{r,echo=FALSE}
v3.k5.BIC
```
###BIC summary 
```{r,echo=FALSE}
BIC1=rbind(v1.k1.BIC,v1.k2.BIC,v1.k3.BIC,v1.k4.BIC,v1.k5.BIC)
BIC2=rbind(v2.k1.BIC, v2.k2.BIC,v2.k3.BIC,v2.k4.BIC,v2.k5.BIC)
BIC3=rbind(v3.k1.BIC, v3.k2.BIC,v3.k3.BIC,v3.k4.BIC,v3.k5.BIC)
BIC=cbind(BIC1,BIC2,BIC3)
colnames(BIC)=c("R1+R2", "R1+R2+R3", "R1+R2+R3+R4")
rownames(BIC)=c("K=1", "K=2","K=3","K=4","K=5")
```
```{r, echo=FALSE}
library(knitr)
kable(BIC)
```
